---
title: "Inclass Assignment 1:Daily Shelter Overnight Occupancy in Feb,2022"
author: "Group 4- Health Informatics Group"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading data and inserting variable
```{r}
DS <- read.csv(file.choose())
```

# Load tidyvese
```{r}
library(tidyverse)
```

# Arithmetic operation between 2 numerical variables  

**(NA Signifies that the shelter is room based and not bed based)**
```{r}
totalbeds= DS$OCCUPIED_BEDS + DS$UNOCCUPIED_BEDS
totalbeds

```

# Logical operator Element-wise logical OR 

**See if Total beds calculated are equal to the capacity (NA Signifies that the shelter is room based and not bed based)**
```{r}
totalbeds|DS$CAPACITY_ACTUAL_BED
```

# Create a new variable
```{r}
VAR12<- 89
VAR12
```

# Convert numerical variable into character
```{r}
typeof(DS$UNAVAILABLE_BEDS)
UB <- (DS$UNAVAILABLE_BEDS)
as.character(UB)
```

# Display today's date and store it in a variable
```{r}
date <- Sys.Date()
date
```

# Print the internal datasets available in R and make one into a variable 
```{r}
ls("package:datasets")
DS2 <- BOD
DS2
```
